Model Comparisons

### 2015-11-29 models/Model_Comparison.Rmd
starting write-up for model comparisons

## Run comparisons
```{r run_comparisons, message=FALSE}
# Save performance output
performance.output = data.frame(model=rep(NA, 16),
                                cor.e6=rep(NA, 16),
                                cor.e11=rep(NA, 16),
                                normalized=rep(NA, 16))
alphas = rep(NA, 16)
data.full.transfer = data.full[matched.items, ]
data.full.transfer$degree =
  ifelse(data.full.transfer$degree == "hi1", "hi", "low")
# Model 1 - Entailment only models
# --------------------------------
# 1.a)
# Entailment only
# Normalized = T
# alpha tuning = F
alphas[1] = 1
m1.a = data.partial %>%
  do(run.partial(., alpha = alphas[1], useprior=T, usenone=F, normalize=T))
# Store output and add e11
m1.a = cbind(m1.a, data.full.transfer$listener.p)
colnames(m1.a)[8] = "e11.listener.p"
performance.output[1, ] = c("m1.a", round(cor(m1.a$listener.p, m1.a$pred), 5),
                            round(cor(m1.a$e11.listener.p, m1.a$pred), 5), T)
# Store plot
m1.a.plot = qplot(stars, listener.p, col=degree, 
      data=m1.a,
      main=paste("m1.a\nalpha: ", alphas[1], "\nNormalized = ", T),
      ylab="Posterior p(rating | word)") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

# 1.b)
# Entailment only
# Normalized = F
# alpha tune = F
alphas[2] = 1
m1.b = data.partial %>%
  do(run.partial(., alpha = alphas[1], useprior=T, usenone=F, normalize=F))
# Store output
m1.b = cbind(m1.b, data.full.transfer$listener.p)
colnames(m1.b)[8] = "e11.listener.p"
performance.output[2, ] = c("m1.b", round(cor(m1.b$listener.p, m1.b$pred), 5),
                            round(cor(m1.b$e11.listener.p, m1.b$pred), 5), T)
# Store plot
m1.b.plot = qplot(stars, listener.p, col=degree, 
      data=m1.b,
      main=paste("m1.b\nalpha: ", alphas[2], "\nNormalized = ", F),
      ylab="Posterior p(rating | word)") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

# 1.c)
# Entailment only
# Normalized = T
# alpha tune = T
alphas[3] = tune.alpha(data.partial, normalize=T, compare.data=data.full.transfer)
m1.c = data.partial %>%
  do(run.partial(., alpha = alphas[3], useprior=T, usenone=F, normalize=T))
# Store output
m1.c = cbind(m1.c, data.full.transfer$listener.p)
colnames(m1.c)[8] = "e11.listener.p"
performance.output[3, ] = c("m1.c", round(cor(m1.c$listener.p, m1.c$pred), 5),
                            round(cor(m1.c$e11.listener.p, m1.c$pred), 5), T)
# Store plot
m1.c.plot = qplot(stars, listener.p, col=degree, 
      data=m1.c,
      main=paste("m1.c\nalpha: ", alphas[3], "\nNormalized = ", T),
      ylab="Posterior p(rating | word)") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

# 1.d)
# Entailment only
# Normalized = F
# alpha tune = T
alphas[4] = tune.alpha(data.partial, normalize=F)
m1.d = data.partial %>%
  do(run.partial(., alpha = alphas[4], useprior=T, usenone=F, normalize=F))
# Store output
m1.d = cbind(m1.d, data.full.transfer$listener.p)
colnames(m1.d)[8] = "e11.listener.p"
performance.output[4, ] = c("m1.d", round(cor(m1.d$listener.p, m1.d$pred), 5),
                            round(cor(m1.d$e11.listener.p, m1.d$pred), 5), normalized=F)
# Store plot
m1.d.plot = qplot(stars, listener.p, col=degree, 
      data=m1.d,
      main=paste("m1.d\nalpha: ", alphas[4], "\nNormalized = ", F),
      ylab="Posterior p(rating | word)") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

# Model 2 - Entailment + generic none
# --------------------------------
# 2.a)
# Entailment + generic None
# Normalized = T
# alpha tuning = F
alphas[5] = 1
m2.a = data.partial %>%
  do(run.partial(., alpha = alphas[5], useprior=T, usenone=T, normalize=T))
# Store output
m2.a = cbind(m2.a, data.full.transfer$listener.p)
colnames(m2.a)[8] = "e11.listener.p"
performance.output[5, ] = c("m2.a", round(cor(m2.a$listener.p, m2.a$pred), 5),
                            round(cor(m2.a$e11.listener.p, m2.a$pred), 5), T)
# Store plot
m2.a.plot = qplot(stars, listener.p, col=degree, 
      data=m2.a,
      main=paste("m2.a\nalpha: ", alphas[5], "\nNormalized = ", T),
      ylab="Posterior p(rating | word)") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

# 2.b)
# Entailment + generic None
# Normalized = F
# alpha tune = F
alphas[6] = 1
m2.b = data.partial %>%
  do(run.partial(., alpha = alphas[6], useprior=T, usenone=T, normalize=F))
# Store output
m2.b = cbind(m2.b, data.full.transfer$listener.p)
colnames(m2.b)[8] = "e11.listener.p"
performance.output[6, ] = c("m2.b", round(cor(m2.b$listener.p, m2.b$pred), 5),
                            round(cor(m2.b$e11.listener.p, m2.b$pred), 5), F)
# Store plot
m2.b.plot = qplot(stars, listener.p, col=degree, 
      data=m2.b,
      main=paste("m2.b\nalpha: ", alphas[6], "\nNormalized = ", F),
      ylab="Posterior p(rating | word)") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

# 2.c)
# Entailment + generic None
# Normalized = T
# alpha tune = T
# compare.data = Toggle this with data.full.transfer for e11 or NULL for e6
alphas[7] = tune.alpha(data.partial, normalize=T, compare.data=NULL)
m2.c = data.partial %>%
  do(run.partial(., alpha = alphas[7], useprior=T, usenone=T, normalize=T))
# Store output
m2.c = cbind(m2.c, data.full.transfer$listener.p)
colnames(m2.c)[8] = "e11.listener.p"
performance.output[7, ] = c("m2.c", round(cor(m2.c$listener.p, m2.c$pred), 5),
                            round(cor(m2.c$e11.listener.p, m2.c$pred), 5), T)
# Store plot
m2.c.plot = qplot(stars, listener.p, col=degree, 
      data=m2.c,
      main=paste("m2.c\nalpha: ", alphas[7], "\nNormalized = ", T),
      ylab="Posterior p(rating | word)") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

# 2.d)
# Entailment + generic None
# Normalized = F
# alpha tune = T
# compare.data = Toggle this with data.full.transfer for e11 or NULL for e6
alphas[8] = tune.alpha(data.partial, normalize=F)
m2.d = data.partial %>%
  do(run.partial(., alpha = alphas[8], useprior=T, usenone=T, normalize=F))
# Store output
m2.d = cbind(m2.d, data.full.transfer$listener.p)
colnames(m2.d)[8] = "e11.listener.p"
performance.output[8, ] = c("m2.d", round(cor(m2.d$listener.p, m2.d$pred), 5),
                            round(cor(m2.d$e11.listener.p, m2.d$pred), 5), F)
# Store plot
m2.d.plot = qplot(stars, listener.p, col=degree, 
      data=m2.d,
      main=paste("m2.d\nalpha: ", alphas[8], "\nNormalized = ", F),
      ylab="Posterior p(rating | word)") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

# Model 3 - Empirical alternatives
# --------------------------------
# 3.a)
# Emp alts
# Normalized = T
# alpha tuning = F
alphas[9] = 1
m3.a = data.full %>%
  do(run.full(., alpha = alphas[9], addMid=F, normalize=T))
# Match with e6 w/ checks
m3.a.matched = m3.a[matched.items, ]
m3.a.matched$degree = ifelse(m3.a.matched$degree == "hi1", "hi", "low")
m3.a.matched = cbind(m3.a.matched, data.partial$listener.p)
all(m3.a.matched$scale == data.partial$scale & m3.a.matched$degree == data.partial$degree)
colnames(m3.a.matched)[length(colnames(m3.a.matched))] = "e6.listener.p"
# Store output
performance.output[9, ] = c("m3.a", round(cor(m3.a.matched$e6.listener.p, m3.a.matched$pred), 5),
                            round(cor(m3.a.matched$listener.p, m3.a.matched$pred), 5), T)
# Store plot
m3.a.plot = qplot(stars, e6.listener.p, col=degree, 
      data=m3.a.matched,
      main=paste("m3.a\nalpha: ", alphas[9], "\nNormalized = ", T),
      ylab="Posterior p(rating | word)") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

# 3.b)
# Emp alts
# Entailment + generic None
# Normalized = F
# alpha tune = F
alphas[10] = 1
m3.b = data.full %>%
  do(run.full(., alpha = alphas[10], addMid=F, normalize=F))
# Match with e6 w/ checks
m3.b.matched = m3.b[matched.items, ]
m3.b.matched$degree = ifelse(m3.b.matched$degree == "hi1", "hi", "low")
m3.b.matched = cbind(m3.b.matched, data.partial$listener.p)
all(m3.b.matched$scale == data.partial$scale & m3.b.matched$degree == data.partial$degree)
colnames(m3.b.matched)[length(colnames(m3.b.matched))] = "e6.listener.p"
# Store output
performance.output[10, ] = c("m3.b", round(cor(m3.b.matched$e6.listener.p, m3.b.matched$pred), 5),
                             round(cor(m3.b.matched$listener.p, m3.b.matched$pred), 5), F)
# Store plot
m3.b.plot = qplot(stars, e6.listener.p, col=degree, 
      data=m3.b.matched,
      main=paste("m3.b\nalpha: ", alphas[10], "\nNormalized = ", F),
      ylab="Posterior p(rating | word)") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

# 3.c)
# Emp alts
# Normalized = T
# alpha tune = T
# compare.data = Toggle this with data.partial for e6 or NULL for e11
alphas[11] = tune.alpha(data.full, type = "full", compare.data=data.partial, addMid=F, normalize=T)
m3.c = data.full %>%
  do(run.full(., alpha = alphas[11], addMid=F, normalize=T))
# Match with e6 w/ checks
m3.c.matched = m3.c[matched.items, ]
m3.c.matched$degree = ifelse(m3.c.matched$degree == "hi1", "hi", "low")
m3.c.matched = cbind(m3.c.matched, data.partial$listener.p)
all(m3.c.matched$scale == data.partial$scale & m3.c.matched$degree == data.partial$degree)
colnames(m3.c.matched)[length(colnames(m3.c.matched))] = "e6.listener.p"
# Store output
performance.output[11, ] = c("m3.c", round(cor(m3.c.matched$e6.listener.p, m3.c.matched$pred), 5),
                             round(cor(m3.c.matched$listener.p, m3.c.matched$pred), 5), T)
# Store plot
m3.c.plot = qplot(stars, e6.listener.p, col=degree, 
      data=m3.c.matched,
      main=paste("m3.c\nalpha: ", alphas[11], "\nNormalized = ", T),
      ylab="Posterior p(rating | word)") +
      ylim(0, 1) +
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

# 3.d)
# Emp alts
# Normalized = F
# alpha tune = T
# compare.data = Toggle this with data.partial or NULL
alphas[12] = tune.alpha(data.full, type = "full", compare.data=data.partial, addMid=F, normalize=F)
m3.d = data.full %>%
  do(run.full(., alpha = alphas[12], addMid=F, normalize=F))
# Match with e6 w/ checks
m3.d.matched = m3.d[matched.items, ]
m3.d.matched$degree = ifelse(m3.d.matched$degree == "hi1", "hi", "low")
m3.d.matched = cbind(m3.d.matched, data.partial$listener.p)
all(m3.d.matched$scale == data.partial$scale & m3.d.matched$degree == data.partial$degree)
colnames(m3.d.matched)[length(colnames(m3.d.matched))] = "e6.listener.p"
# Store output
performance.output[12, ] = c("m3.d", round(cor(m3.d.matched$e6.listener.p, m3.d.matched$pred), 5),
                             round(cor(m3.d.matched$listener.p, m3.d.matched$pred), 5), F)
# Store plot
m3.d.plot = qplot(stars, e6.listener.p, col=degree, 
      data=m3.d.matched,
      main=paste("m3.d\nalpha: ", alphas[12], "\nNormalized = ", F),
      ylab="Posterior p(rating | word)") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

# Model 4 - Empirical alternatives + extras
# -----------------------------------------
# 4.a)
# Emp alts + extras
# Normalized = T
# alpha tuning = F
alphas[13] = 1
m4.a = data.full.extras %>%
  do(run.full(., alpha = alphas[13], addMid=T, normalize=T))
# Match with e6 w/ checks
m4.a.matched = m4.a[matched.items.extras, ]
m4.a.matched$degree = ifelse(m4.a.matched$degree == "hi1", "hi", "low")
m4.a.matched = cbind(m4.a.matched, data.partial$listener.p)
all(m4.a.matched$scale == data.partial$scale & m4.a.matched$degree == data.partial$degree)
colnames(m4.a.matched)[length(colnames(m4.a.matched))] = "e6.listener.p"
# Store output
performance.output[13, ] = c("m4.a", round(cor(m4.a.matched$e6.listener.p, m4.a.matched$pred), 5), 
                             round(cor(m4.a.matched$listener.p, m4.a.matched$pred), 5), T)
# Store plot
m4.a.plot = qplot(stars, e6.listener.p, col=degree, 
      data=m4.a.matched,
      main=paste("m4.a\nalpha: ", alphas[13], "\nNormalized = ", T),
      ylab="Posterior p(rating | word)") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

# 4.b)
# Emp alts + extras
# Normalized = F
# alpha tune = F
alphas[14] = 1
m4.b = data.full.extras %>%
  do(run.full(., alpha = alphas[14], addMid=T, normalize=F))
# Match with e6 w/ checks
m4.b.matched = m4.b[matched.items.extras, ]
m4.b.matched$degree = ifelse(m4.b.matched$degree == "hi1", "hi", "low")
m4.b.matched = cbind(m4.b.matched, data.partial$listener.p)
all(m4.b.matched$scale == data.partial$scale & m4.b.matched$degree == data.partial$degree)
colnames(m4.b.matched)[length(colnames(m4.b.matched))] = "e6.listener.p"
# Store output
performance.output[14, ] = c("m4.b", round(cor(m4.b.matched$e6.listener.p, m4.b.matched$pred), 5), 
                             round(cor(m4.b.matched$listener.p, m4.b.matched$pred), 5), F)
# Store plot
m4.b.plot = qplot(stars, e6.listener.p, col=degree, 
      data=m4.b.matched,
      main=paste("m4.b\nalpha: ", alphas[14], "\nNormalized = ", F),
      ylab="Posterior p(rating | word)") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

@@

# Store plot
m4.c.plot = qplot(stars, listener.p, col=degree, 
      data=m4.c.matched,
      main=paste("m4.c\nalpha: ", alphas[15], "\nNormalized = ", T),
      ylab="Posterior p(rating | word)") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

# 4.d)
# Emp alts + extras
# Normalized = F
# alpha tune = T
# compare.data = Toggle this with data.partial or NULL
alphas[16] = tune.alpha(data.full.extras, type = "full", compare.data=data.partial, addMid=T, normalize=F)
m4.d = data.full.extras %>%
  do(run.full(., alpha = alphas[16], addMid=T, normalize=F))
# Match with e6 w/ checks
m4.d.matched = m4.d[matched.items.extras, ]
m4.d.matched$degree = ifelse(m4.d.matched$degree == "hi1", "hi", "low")
m4.d.matched = cbind(m4.d.matched, data.partial$listener.p)
all(m4.d.matched$scale == data.partial$scale & m4.d.matched$degree == data.partial$degree)
colnames(m4.d.matched)[length(colnames(m4.d.matched))] = "e6.listener.p"
# Store output
performance.output[16, ] = c("m4.d", round(cor(m4.d.matched$e6.listener.p, m4.d.matched$pred), 5),
                             round(cor(m4.d.matched$listener.p, m4.d.matched$pred), 5), F)
# Store plot
m4.d.plot = qplot(stars, e6.listener.p, col=degree, 
      data=m4.d.matched,
      main=paste("m4.d\nalpha: ", alphas[16], "\nNormalized = ", F),
      ylab="Posterior p(rating | word)") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

>>>>

## Run comparisons
```{r run_comparisons, message=FALSE}
# Save performance output
performance.output = data.frame(model=rep(NA, 16),
                                cor.e6=rep(NA, 16),
                                cor.e11=rep(NA, 16),
                                normalized=rep(NA, 16))
alphas = rep(NA, 16)
data.full.transfer = data.full[matched.items, ]
data.full.transfer$degree =
  ifelse(data.full.transfer$degree == "hi1", "hi", "low")
# Model 1 - Entailment only models
# --------------------------------
# 1.a)
# Entailment only
# Normalized = T
# alpha tuning = F
alphas[1] = 1
m1.a = data.partial %>%
  do(run.partial(., alpha = alphas[1], useprior=T, usenone=F, normalize=T))
# Store output and add e11
m1.a = cbind(m1.a, data.full.transfer$listener.p)
colnames(m1.a)[8] = "e11.listener.p"
performance.output[1, ] = c("m1.a", round(cor(m1.a$listener.p, m1.a$pred), 5),
                            round(cor(m1.a$e11.listener.p, m1.a$pred), 5), T)
# Store plot
m1.a.plot = qplot(stars, listener.p, col=degree, 
      data=m1.a,
      main=paste("m1.a\nalpha: ", alphas[1],
                 "\nNormalized = ", T,
                 "\nCorr = ", performance.output[1, 2]),
      ylab="Posterior p(rating | word)") + 
  ylim(0, 1) +
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

# 1.b)
# Entailment only
# Normalized = F
# alpha tune = F
alphas[2] = 1
m1.b = data.partial %>%
  do(run.partial(., alpha = alphas[1], useprior=T, usenone=F, normalize=F))
# Store output
m1.b = cbind(m1.b, data.full.transfer$listener.p)
colnames(m1.b)[8] = "e11.listener.p"
performance.output[2, ] = c("m1.b", round(cor(m1.b$listener.p, m1.b$pred), 5),
                            round(cor(m1.b$e11.listener.p, m1.b$pred), 5), F)
# Store plot
m1.b.plot = qplot(stars, listener.p, col=degree, 
      data=m1.b,
      main=paste("m1.b\nalpha: ", alphas[2],
                 "\nNormalized = ", F,
                 "\nCorr = ", performance.output[2, 2]),
      ylab="Posterior p(rating | word)") + 
  ylim(0, 1) +
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

# 1.c)
# Entailment only
# Normalized = T
# alpha tune = T
alphas[3] = tune.alpha(data.partial, normalize=T, compare.data=data.full.transfer)
m1.c = data.partial %>%
  do(run.partial(., alpha = alphas[3], useprior=T, usenone=F, normalize=T))
# Store output
m1.c = cbind(m1.c, data.full.transfer$listener.p)
colnames(m1.c)[8] = "e11.listener.p"
performance.output[3, ] = c("m1.c", round(cor(m1.c$listener.p, m1.c$pred), 5),
                            round(cor(m1.c$e11.listener.p, m1.c$pred), 5), T)
# Store plot
m1.c.plot = qplot(stars, listener.p, col=degree, 
      data=m1.c,
      main=paste("m1.c\nalpha: ", alphas[3],
                 "\nNormalized = ", T,
                 "\nCorr = ", performance.output[3, 2]),
      ylab="Posterior p(rating | word)") + 
  ylim(0, 1) +
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

# 1.d)
# Entailment only
# Normalized = F
# alpha tune = T
alphas[4] = tune.alpha(data.partial, normalize=F)
m1.d = data.partial %>%
  do(run.partial(., alpha = alphas[4], useprior=T, usenone=F, normalize=F))
# Store output
m1.d = cbind(m1.d, data.full.transfer$listener.p)
colnames(m1.d)[8] = "e11.listener.p"
performance.output[4, ] = c("m1.d", round(cor(m1.d$listener.p, m1.d$pred), 5),
                            round(cor(m1.d$e11.listener.p, m1.d$pred), 5), normalized=F)
# Store plot
m1.d.plot = qplot(stars, listener.p, col=degree, 
      data=m1.d,
      main=paste("m1.d\nalpha: ", alphas[4],
                 "\nNormalized = ", F,
                 "\nCorr = ", performance.output[4, 2]),
      ylab="Posterior p(rating | word)") + 
  ylim(0, 1) +
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

# Model 2 - Entailment + generic none
# --------------------------------
# 2.a)
# Entailment + generic None
# Normalized = T
# alpha tuning = F
alphas[5] = 1
m2.a = data.partial %>%
  do(run.partial(., alpha = alphas[5], useprior=T, usenone=T, normalize=T))
# Store output
m2.a = cbind(m2.a, data.full.transfer$listener.p)
colnames(m2.a)[8] = "e11.listener.p"
performance.output[5, ] = c("m2.a", round(cor(m2.a$listener.p, m2.a$pred), 5),
                            round(cor(m2.a$e11.listener.p, m2.a$pred), 5), T)
# Store plot
m2.a.plot = qplot(stars, listener.p, col=degree, 
      data=m2.a,
      main=paste("m2.a\nalpha: ", alphas[5],
                 "\nNormalized = ", T,
                 "\nCorr = ", performance.output[5, 2]),
      ylab="Posterior p(rating | word)") + 
  ylim(0, 1) +
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

# 2.b)
# Entailment + generic None
# Normalized = F
# alpha tune = F
alphas[6] = 1
m2.b = data.partial %>%
  do(run.partial(., alpha = alphas[6], useprior=T, usenone=T, normalize=F))
# Store output
m2.b = cbind(m2.b, data.full.transfer$listener.p)
colnames(m2.b)[8] = "e11.listener.p"
performance.output[6, ] = c("m2.b", round(cor(m2.b$listener.p, m2.b$pred), 5),
                            round(cor(m2.b$e11.listener.p, m2.b$pred), 5), F)
# Store plot
m2.b.plot = qplot(stars, listener.p, col=degree, 
      data=m2.b,
      main=paste("m2.b\nalpha: ", alphas[6],
                 "\nNormalized = ", F,
                 "\nCorr = ", performance.output[6, 2]),
      ylab="Posterior p(rating | word)") + 
  ylim(0, 1) +
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

# 2.c)
# Entailment + generic None
# Normalized = T
# alpha tune = T
# compare.data = Toggle this with data.full.transfer for e11 or NULL for e6
alphas[7] = tune.alpha(data.partial, normalize=T, compare.data=NULL)
m2.c = data.partial %>%
  do(run.partial(., alpha = alphas[7], useprior=T, usenone=T, normalize=T))
# Store output
m2.c = cbind(m2.c, data.full.transfer$listener.p)
colnames(m2.c)[8] = "e11.listener.p"
performance.output[7, ] = c("m2.c", round(cor(m2.c$listener.p, m2.c$pred), 5),
                            round(cor(m2.c$e11.listener.p, m2.c$pred), 5), T)
# Store plot
m2.c.plot = qplot(stars, listener.p, col=degree, 
      data=m2.c,
      main=paste("m2.c\nalpha: ", alphas[7],
                 "\nNormalized = ", T,
                 "\nCorr = ", performance.output[7, 2]),
      ylab="Posterior p(rating | word)") + 
  ylim(0, 1) +
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

# 2.d)
# Entailment + generic None
# Normalized = F
# alpha tune = T
# compare.data = Toggle this with data.full.transfer for e11 or NULL for e6
alphas[8] = tune.alpha(data.partial, normalize=F)
m2.d = data.partial %>%
  do(run.partial(., alpha = alphas[8], useprior=T, usenone=T, normalize=F))
# Store output
m2.d = cbind(m2.d, data.full.transfer$listener.p)
colnames(m2.d)[8] = "e11.listener.p"
performance.output[8, ] = c("m2.d", round(cor(m2.d$listener.p, m2.d$pred), 5),
                            round(cor(m2.d$e11.listener.p, m2.d$pred), 5), F)
# Store plot
m2.d.plot = qplot(stars, listener.p, col=degree, 
      data=m2.d,
      main=paste("m2.d\nalpha: ", alphas[8],
                 "\nNormalized = ", F,
                 "\nCorr = ", performance.output[8, 2]),
      ylab="Posterior p(rating | word)") + 
  ylim(0, 1) +
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

# Model 3 - Empirical alternatives
# --------------------------------
# 3.a)
# Emp alts
# Normalized = T
# alpha tuning = F
alphas[9] = 1
m3.a = data.full %>%
  do(run.full(., alpha = alphas[9], addMid=F, normalize=T))
# Match with e6 w/ checks
m3.a.matched = m3.a[matched.items, ]
m3.a.matched$degree = ifelse(m3.a.matched$degree == "hi1", "hi", "low")
m3.a.matched = cbind(m3.a.matched, data.partial$listener.p)
all(m3.a.matched$scale == data.partial$scale & m3.a.matched$degree == data.partial$degree)
colnames(m3.a.matched)[length(colnames(m3.a.matched))] = "e6.listener.p"
# Store output
performance.output[9, ] = c("m3.a", round(cor(m3.a.matched$e6.listener.p, m3.a.matched$pred), 5),
                            round(cor(m3.a.matched$listener.p, m3.a.matched$pred), 5), T)
# Store plot
m3.a.plot = qplot(stars, e6.listener.p, col=degree, 
      data=m3.a.matched,
      main=paste("m3.a\nalpha: ", alphas[9],
                 "\nNormalized = ", T,
                 "\nCorr = ", performance.output[9, 2]),
      ylab="Posterior p(rating | word)") + 
  ylim(0, 1) +
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

# 3.b)
# Emp alts
# Entailment + generic None
# Normalized = F
# alpha tune = F
alphas[10] = 1
m3.b = data.full %>%
  do(run.full(., alpha = alphas[10], addMid=F, normalize=F))
# Match with e6 w/ checks
m3.b.matched = m3.b[matched.items, ]
m3.b.matched$degree = ifelse(m3.b.matched$degree == "hi1", "hi", "low")
m3.b.matched = cbind(m3.b.matched, data.partial$listener.p)
all(m3.b.matched$scale == data.partial$scale & m3.b.matched$degree == data.partial$degree)
colnames(m3.b.matched)[length(colnames(m3.b.matched))] = "e6.listener.p"
# Store output
performance.output[10, ] = c("m3.b", round(cor(m3.b.matched$e6.listener.p, m3.b.matched$pred), 5),
                             round(cor(m3.b.matched$listener.p, m3.b.matched$pred), 5), F)
# Store plot
m3.b.plot = qplot(stars, e6.listener.p, col=degree, 
      data=m3.b.matched,
      main=paste("m3.b\nalpha: ", alphas[10],
                 "\nNormalized = ", F,
                 "\nCorr = ", performance.output[10, 2]),
      ylab="Posterior p(rating | word)") + 
  ylim(0, 1) +
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

# 3.c)
# Emp alts
# Normalized = T
# alpha tune = T
# compare.data = Toggle this with data.partial for e6 or NULL for e11
alphas[11] = tune.alpha(data.full, type = "full", compare.data=data.partial, addMid=F, normalize=T)
m3.c = data.full %>%
  do(run.full(., alpha = alphas[11], addMid=F, normalize=T))
# Match with e6 w/ checks
m3.c.matched = m3.c[matched.items, ]
m3.c.matched$degree = ifelse(m3.c.matched$degree == "hi1", "hi", "low")
m3.c.matched = cbind(m3.c.matched, data.partial$listener.p)
all(m3.c.matched$scale == data.partial$scale & m3.c.matched$degree == data.partial$degree)
colnames(m3.c.matched)[length(colnames(m3.c.matched))] = "e6.listener.p"
# Store output
performance.output[11, ] = c("m3.c", round(cor(m3.c.matched$e6.listener.p, m3.c.matched$pred), 5),
                             round(cor(m3.c.matched$listener.p, m3.c.matched$pred), 5), T)
# Store plot
m3.c.plot = qplot(stars, e6.listener.p, col=degree, 
      data=m3.c.matched,
      main=paste("m3.c\nalpha: ", alphas[11],
                 "\nNormalized = ", T,
                 "\nCorr = ", performance.output[11, 2]),
      ylab="Posterior p(rating | word)") +
      ylim(0, 1) +
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

# 3.d)
# Emp alts
# Normalized = F
# alpha tune = T
# compare.data = Toggle this with data.partial or NULL
alphas[12] = tune.alpha(data.full, type = "full", compare.data=data.partial, addMid=F, normalize=F)
m3.d = data.full %>%
  do(run.full(., alpha = alphas[12], addMid=F, normalize=F))
# Match with e6 w/ checks
m3.d.matched = m3.d[matched.items, ]
m3.d.matched$degree = ifelse(m3.d.matched$degree == "hi1", "hi", "low")
m3.d.matched = cbind(m3.d.matched, data.partial$listener.p)
all(m3.d.matched$scale == data.partial$scale & m3.d.matched$degree == data.partial$degree)
colnames(m3.d.matched)[length(colnames(m3.d.matched))] = "e6.listener.p"
# Store output
performance.output[12, ] = c("m3.d", round(cor(m3.d.matched$e6.listener.p, m3.d.matched$pred), 5),
                             round(cor(m3.d.matched$listener.p, m3.d.matched$pred), 5), F)
# Store plot
m3.d.plot = qplot(stars, e6.listener.p, col=degree, 
      data=m3.d.matched,
      main=paste("m3.d\nalpha: ", alphas[12],
                 "\nNormalized = ", F,
                 "\nCorr = ", performance.output[12, 2]),
      ylab="Posterior p(rating | word)") + 
  ylim(0, 1) +
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

# Model 4 - Empirical alternatives + extras
# -----------------------------------------
# 4.a)
# Emp alts + extras
# Normalized = T
# alpha tuning = F
alphas[13] = 1
m4.a = data.full.extras %>%
  do(run.full(., alpha = alphas[13], addMid=T, normalize=T))
# Match with e6 w/ checks
m4.a.matched = m4.a[matched.items.extras, ]
m4.a.matched$degree = ifelse(m4.a.matched$degree == "hi1", "hi", "low")
m4.a.matched = cbind(m4.a.matched, data.partial$listener.p)
all(m4.a.matched$scale == data.partial$scale & m4.a.matched$degree == data.partial$degree)
colnames(m4.a.matched)[length(colnames(m4.a.matched))] = "e6.listener.p"
# Store output
performance.output[13, ] = c("m4.a", round(cor(m4.a.matched$e6.listener.p, m4.a.matched$pred), 5), 
                             round(cor(m4.a.matched$listener.p, m4.a.matched$pred), 5), T)
# Store plot
m4.a.plot = qplot(stars, e6.listener.p, col=degree, 
      data=m4.a.matched,
      main=paste("m4.a\nalpha: ", alphas[13],
                 "\nNormalized = ", T,
                 "\nCorr = ", performance.output[13, 2]),
      ylab="Posterior p(rating | word)") + 
  ylim(0, 1) +
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

# 4.b)
# Emp alts + extras
# Normalized = F
# alpha tune = F
alphas[14] = 1
m4.b = data.full.extras %>%
  do(run.full(., alpha = alphas[14], addMid=T, normalize=F))
# Match with e6 w/ checks
m4.b.matched = m4.b[matched.items.extras, ]
m4.b.matched$degree = ifelse(m4.b.matched$degree == "hi1", "hi", "low")
m4.b.matched = cbind(m4.b.matched, data.partial$listener.p)
all(m4.b.matched$scale == data.partial$scale & m4.b.matched$degree == data.partial$degree)
colnames(m4.b.matched)[length(colnames(m4.b.matched))] = "e6.listener.p"
# Store output
performance.output[14, ] = c("m4.b", round(cor(m4.b.matched$e6.listener.p, m4.b.matched$pred), 5), 
                             round(cor(m4.b.matched$listener.p, m4.b.matched$pred), 5), F)
# Store plot
m4.b.plot = qplot(stars, e6.listener.p, col=degree, 
      data=m4.b.matched,
      main=paste("m4.b\nalpha: ", alphas[14],
                 "\nNormalized = ", F,
                 "\nCorr = ", performance.output[14, 2]),
      ylab="Posterior p(rating | word)") + 
  ylim(0, 1) +
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

@@

# Store plot
m4.c.plot = qplot(stars, listener.p, col=degree, 
      data=m4.c.matched,
      main=paste("m4.c\nalpha: ", alphas[15],
                 "\nNormalized = ", T,
                 "\nCorr = ", performance.output[15, 2]),
      ylab="Posterior p(rating | word)") + 
  ylim(0, 1) +
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)
